%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
 % 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Hang}{Yuan}{ \urlstyle{same}\url{http://angerhang.github.io} \\
\href{mailto:h.yuan@jacobs-university.de}{h.yuan@jacobs-university.de} | +49 157 877 06732 | Campus Ring 1, Bremen, Germany, 28759
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{\normalsize{Carnegie Mellon University}}
\descript{\small{Exchange at School of Computer Science}}
\location{Fall | Pittsburgh, USA}
\sectionsep

\subsection{Jacobs University}
\descript{Bachelor in Computer Science}
\location{Aug 2014 - June 2017 | Bremen, Germany}
\sectionsep

\subsection{Valley Christian HS}
\location{Aug 2012 - May 2014 | Los Angeles, USA}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{School Courses}
Software Engineering and its Lab \\
Programming in Java \\
Programming in C++ \\
Computability and Complexity \\
Formal Language and Logic \\
Computer Architecture \\ 
Linear Algebra \\
Applied Differential Equations \\ 
Decision Making
 
\sectionsep

\subsection{Open Courses (MOOCs)}
{\large Stanford}: \\
Machine Learning (ML) \\

\sectionsep
{\large University of Washington}:  \\
ML Foundations  \\
ML Regressions  \\
ML Classification

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Comfortable}
Java \textbullet{}   C/C++ \textbullet{} R \textbullet{} Python \textbullet \LaTeX \\
\location{Basic}
Matlab \textbullet{} SML \textbullet{} Emacs \textbullet{} Shell \textbullet{} iOS \\

\sectionsep

\subsection{Languages}
Chinese (native) \textbullet{}  English (fluent) \\
German (basic) \textbullet{}   Spanish (basic)

\sectionsep

\section{Hobbies}
\location{Clarinet 10 years}
\textbullet{}  Bremer Orchester Gemeinschaft 2015 \\
%\textbullet{} Valley Christian High School Band and Orchestra 
%Section Leader 2013 - 2014 \\
\location{Tennis 10 years}
\textbullet{} High School Tennis Varsity \\
\textbullet{} Most Inspirational Player (School wide) 2014 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{KPMG Data Observatory, Imperial College}
\descript{| Research Intern}
\location{June 2016 – Present | London, The United Kingdom}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Created visualizations about London city crime and transport to the local governors on the 64 HD 
screens panoramic observatory in C\#. 
\item Simulated large-scale 3D models, including
oil flow in Saudi Arabia and atom collision in a nuclear power plant in a distributed fashion using Unity. 
\end{tightemize}
\sectionsep

\runsubsection{KWARC Research Group}
\descript{| Research Assistant under prof. Michael Kohlhase}
\location{Dec 2014 - Present | Bremen, Germany}
\begin{tightemize}
\item Developed Semantic \TeX \ (sTeX) LaTeXML plugin which transfers 
 s\TeX\ to OMDoc in perl.
 \item Contributed to the mixing the Module Mathematical Theories and sTeX
 as surface languages (publication on CICM will soon become available).
\end{tightemize}

\sectionsep

\runsubsection{Jacobs University}
\descript{| Research Assistant under prof. Adalbert F.X. Wilhelm}
\location{Sep 2015 - May 2016 | Bremen, Germany}
\begin{tightemize}
\item  Benchmarked distributed computing frameworks.
\item Held weekly tutorials on statistics and compiled a tutorial series on R.
\end{tightemize}
\sectionsep

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Research}
%\runsubsection{Cornell Robot Learning Lab}
%\descript{| Head Undergrad Research}
%\location{Jan 2014 – Present | Ithaca, NY}
%Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  Publication submitted.
%\sectionsep
%
%\runsubsection{Cornell Phonetics Lab}
%\descript{| Head Undergraduate Researcher}
%\location{Mar 2012 – May 2013 | Ithaca, NY}
%Lead the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. Publication submitted.
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards and Fundings} 
\awards{\textbf{Second Place  top 10\%} OpenBank Hackathon} 
\Alocation{Jul 2016 | Google London Campus, The United Kingdom}
\begin{tightemize}
\item Bytebit: selling Wifi using Bitcoins via micro-transactions in real time 
 and got invited to pitch at London FinTech week's innovator panel.
\end{tightemize}

\sectionsep

\awards{Wiki Data Prize HPI Machine Learning and Data Analytics Hackathon}
\Alocation{Jun 2016 | Berlin, Germany}
\begin{verytightemize}
\item ShowcaseData: created a data quality metric model for Wiki Data's open source databases.
\end{verytightemize}

\sectionsep
\awards{ERASMUS+ Traineeship}
\Alocation{Jun 2016 | Bremen, Germany}
\begin{verytightemize}
\item 450 euros per month for my internship in the UK.
\end{verytightemize}

\sectionsep
\awards{Promos Scholar}
\Alocation{Jun 2016 | Bremen, Germany}
\begin{verytightemize}
\item 1900 euros for the exchange semester at Carnegie Mellon University.
\end{verytightemize}

\sectionsep
\awards{Global Jacobs Startup Competition \textbf{top 10/130+ 8\%}}
\Alocation{Mar 2015 | Bremen, Germany}
\begin{verytightemize}
\item Developed an application called MyNow for the competition.
MyNow is a time management and social network app that allows users to 
track their time and interact with their friends. (on Apple Apps Store) 
\end{verytightemize}

\sectionsep
\awards{Jacobs University Entrance Scholarship}
\Alocation{Sep 2014 | Bremen, Germany}
\begin{verytightemize}
\item  Merit-based scholarship for academic excellence that last for three years
\end{verytightemize}


\sectionsep
\awards{Daniel Award for International Student Leadership 1/100+ top 1\%}
\Alocation{Apr 2014 | Los Angeles, USA}
\begin{verytightemize}
\item  One international students was selected
for demonstration of leadership. 
\end{verytightemize}

\end{minipage} 
\end{document}  \documentclass[]{article}


